Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-02-13 RNARedPrint-Bioinfo2018.tex
Minor?

\title[short Title]{Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures}
\author[Hammer, Ponty, Wang and Will]{Stefan Hammer\,$^{\text{\sfb 1,2,3}}$, Yann Ponty\,$^{\text{\sfb 4,5,}\star}$, Wei Wang\,$^{\text{\sfb 4}}$ and Sebastian Will\,$^{\text{\sfb 2}}$}
\address{$^{\text{\sf 1}}$University Leipzig, Department of Computer Science and Interdisciplinary Center for Bioinformatics, 04107 Leipzig, Germany; 
$^{\text{\sf 2}}$University of Vienna, Faculty of Chemistry, Department of Theoretical Chemistry, 1090 Vienna, Austria;
$^{\text{\sf 3}}$University of Vienna, Faculty of Computer Science, Research Group Bioinformatics and
Computational Biology, 1090 Vienna, Austria;
$^{\text{\sf 4}}$CNRS UMR 7161 LIX, Ecole Polytechnique, Bat. Turing, 91120 Palaiseau, France;
and $^{\text{\sf 5}}$ AMIBio team, Inria Saclay, Bat Alan Turing, 91120 Palaiseau, France}

@@

\begin{theorem}[Partition function and sampling complexity]
  For sequence length $n$, $k$ target structures, treewidth $w$ and
  a compatibility graph having $c$ connected components, $t$ sequences
  are sampled from the Boltzmann distribution  in
  %$O( n\, k \min(2^{w+c+1},4^{w+1}) + t\, n\, k )$ time.
  $\mathcal{O}( 2^d\, n\, k  + t\, n\, k )$ time, where $d:=\min(w+c+1,2(w+1))$.
\end{theorem}

>>>>

\title[Parameterized multi-target RNA design ]{Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures}
\author[Hammer, Ponty, Wang and Will]{Stefan Hammer\,$^{\text{\sfb 1,2,3}}$, Yann Ponty\,$^{\text{\sfb 4,5,}\star}$, Wei Wang\,$^{\text{\sfb 4}}$ and Sebastian Will\,$^{\text{\sfb 2}}$}
\address{$^{\text{\sf 1}}$University Leipzig, Department of Computer Science and Interdisciplinary Center for Bioinformatics, 04107 Leipzig, Germany; 
$^{\text{\sf 2}}$University of Vienna, Faculty of Chemistry, Department of Theoretical Chemistry, 1090 Vienna, Austria;
$^{\text{\sf 3}}$University of Vienna, Faculty of Computer Science, Research Group Bioinformatics and
Computational Biology, 1090 Vienna, Austria;
$^{\text{\sf 4}}$CNRS UMR 7161 LIX, Ecole Polytechnique, Bat. Turing, 91120 Palaiseau, France;
and $^{\text{\sf 5}}$ AMIBio team, Inria Saclay, Bat Alan Turing, 91120 Palaiseau, France}

@@

\begin{theorem}[Complexities]
  For sequence length $n$, $k$ target structures, treewidth $w$ and
  a compatibility graph having $c$ connected components, $t$ sequences
  are sampled from the Boltzmann distribution  in
  %$O( n\, k \min(2^{w+c+1},4^{w+1}) + t\, n\, k )$ time.
  $\mathcal{O}( 2^d\, n\, k  + t\, n\, k )$ time, where $d:=\min(w+c+1,2(w+1))$.
\end{theorem}
